Outline

### 2020-06-16 Outline.Rmd
merges map creating
adds new idea
adds new set of ideas

### 2. Existing packages
- Basic spatial data
    - Basic data types (i.e. vector vs. raster data)
        - raster, stars, terra(?)
        - sp, sf
        - rgeos, rgdal
        - ...
    - Creating maps
        - maptools, tmap, ggplot2
        - ...
- Web-mapping frameworks
    - mapview, leaflet
    - ...
- Spatial regression
    - nlme, spdep, kriging
    - ...
- Ecological analysis
    - Landscape metrics
        - landscapmetrics
        - ...
    - Habitat selection and SDM
        - ade4, sdm
        - ...
    - Various
        - vegan
        - NLMR
    - ...
- ...
### 3. Missing packages
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...

>>>>

### 2. Existing packages

- Base R
- Basic spatial data
    - Basic data types (i.e. vector vs. raster data)
        - raster, stars, terra(?)
        - sp (+rgeos, rgdal), sf
        - ...
- Creating maps
    - tmap, ggplot2
    - mapview, leaflet
    - ...
- Spatial regression
    - nlme, spdep, gstat
    - ...
- Spatial statistics?? (point-patterns analysis)
    - spatstat
- Ecological analysis
    - Landscape metrics
        - landscapmetrics
        - belg
        - ...
    - Habitat selection and SDM
        - lm(), glm(), gam, RandomForest (ranger)
        - ade4, sdm
        - biomod2??
        - ...
    - Various
        - vegan
        - NLMR, landscapetools
        - ecospat?? (https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02671)
        - PresenceAbsence?? (https://www.jstatsoft.org/article/view/v023i11)
        - ENMeval?? (https://cran.r-project.org/web/packages/ENMeval/index.html)
        - prioritizr?? (https://prioritizr.net/)
        - data sources/API connections?
    - ...
- ...
### 3. Missing packages
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...
